\documentclass[12pt, preprint]{hacked-aastex}
\usepackage{titlesec, hyperref, mdwlist, wrapfig, mdframed, enumitem}

\newenvironment{ditemize}
{ \begin{list}{}{%
\setlength{\topsep}{0pt}% 
\setlength{\partopsep}{3pt}% 
\setlength{\itemsep}{1pt}\setlength{\parsep}{1pt}% 
\setlength{\itemindent}{0pt}\setlength{\listparindent}{12pt}%
\setlength{\leftmargin}{24pt}\setlength{\rightmargin}{0in}%
\setlength{\labelsep}{6pt}\setlength{\labelwidth}{6pt}%
\renewcommand{\makelabel}{\makebox[\labelwidth][l]{$\bullet$\hspace{\fill}}}}}
{\end{list}}

\begin{document}

\pagestyle{plain}
\titlespacing*{\section}{0pt}{0pt}{0.5\baselineskip}
\titlespacing*{\subsection}{0pt}{0.5\baselineskip}{0.5\baselineskip}
%\titleformat{\section}{\bfseries}{\thesection.}{1em}{} 

\newcommand{\imtxt}[1]{\textcolor{red}{#1}}
\newcommand{\imsout}[1]{\textcolor{red}{\sout{#1}}}
\newcommand{\sersic}{S\'{e}rsic}
\setlist[itemize]{leftmargin=*}

\title{{\large Characterizing the local population of \\
mid-infrared-emitting active galactic nuclei}
\\
\large Expertise \& Resources --- Not Anonymized} 

\maketitle

\section{Team Members}\label{sec:team}

\begin{itemize}
\item PI: Michael R. Blanton, Professor, New York University. The 
PI is an expert in nearby galaxies and modeling their spectral
energy distributions (SEDs). He will supervise the graduate student
and contribute to the data analysis, writing, and interpretation.
\item Graduate Student: Arjun Suresh, Ph.D. student, New York University.
Suresh will enter his second year of the Ph.D. program in Fall 2023.
He has experience handling astronomical data and performing likelihood
analyses.
\item Undergraduate Student: Aashay Pai, New York University. Pai 
will enter his senior year in Fall 2023. They are learning how 
to analyze astronomical data and to develop software.
\end{itemize}

\clearpage
\section{Facilities \& Equipment}\label{sec:facilities}

\begin{itemize}
\item{\textit{Observational Resources}---Participating institution in Sloan Digital Sky Survey V, with full data and publication rights for the PI and their students.}
\item{\textit{Systems administration}---The Center for Cosmology and Particle Physics (CCPP) has a Ph.D. as its Systems Administrator who assists with scientific computing issues; his responsibilities include management of the Cluster as well as other CCPP computer systems. The Physics Department has two systems administrators who provide backup assistance for research and administrative computing.}
\item{\textit{Computing hardware}---A high performance computing server room, with liquid-cooled racks and monitoring equipment. Suitable for housing computing resources and with available
servers.
A variety of computing resources are available within CCPP and the Physics Department, including UNIX workstations, laser color printers, etc. Computational needs are also supported through the University's Academic Computing Services, which has a variety of computing platforms and scientific software. Consultants are also available to assist in the use of these resources.}
\item{\textit{Office}---The offices of the PI and other personnel are in the Center for Cosmology and Particle Physics located at New York University.}
\end{itemize}

\clearpage
\section{Summary of Personnel \& Work Effort}\label{sec:effort}

\begin{table}[h!]
\centering
\caption{Personnel and Work Effort (all project years)\label{table:effort}} 
%\caption{Table of Work Effort\label{table:effort}} 
\begin{tabular}{lccc}
\\
\hline
& {\bf Funded Effort} & {\bf Unfunded Effort} & {\bf Total Effort} \\
{\bf Name \& Role} & {\bf (months / year)} & {\bf (months / year)} 
& {\bf (months / year)} \\
\hline
\hline
Michael R. Blanton, PI & 1 & 0 & 1 \\
Arjun Suresh, Grad. Stud. & 12 & 0 & 12 \\
Aashay Pai, Undergrad. Stud. & 2 & 0 & 2 \\
\hline
\end{tabular}
\end{table}

\clearpage
\section{Biographical Sketch: Michael R. Blanton}\label{sec:bio}

\vspace{-0.1in}
\subsection*{\normalsize Professional Preparation:}
\begin{tabular}{@{}l@{\qquad}l@{\qquad}l}
Cornell University & Engineering Physics & BS 1995\\
Princeton University & Astrophysics & PhD 1999\\
Fermi National Accelerator Laboratory & Astrophysics & 1999--2001\\
New York University & Astrophysics & 2001--present
\end{tabular}
           
\vspace{-0.1in}
\subsection*{\normalsize Appointments:}
\begin{tabular}{@{}l@{\qquad}l@{\qquad}l}
Professor & Department of Physics & New York University,
2018--present\\
Associate Professor & Department of Physics & New York University,
2011--2018\\
Assistant Professor & Department of Physics & New York University,
2005--2011\\
Research Scientist & Department of Physics & New York University,
2001--2005\\
Postdoc & Astrophysics & Fermi National Accelerator Lab, 1999--2001
\end{tabular}

\vspace{-0.1in}
\subsection*{\normalsize Five Publications Closely Related to Proposed Project:}
\begin{ditemize}\setlength{\itemsep}{0pt}
\item 
{Blanton}, M.~R., et al.~
% {Bershady}, M.~A., {Abolfathi}, B., {Albareti},
  % F.~D., {Allende Prieto}, C., {Almeida}, A., {Alonso-Garc{\'{\i}}a}, J.,
  % {Anders}, F., {Anderson}, S.~F., {Andrews}, B., {Aquino-Ort{\'{\i}}z}, E.,
  % {Arag{\'o}n-Salamanca}, A., {Argudo-Fern{\'a}ndez}, M., {Armengaud}, E.,
  % {Aubourg}, E., {Avila-Reese}, V., {Badenes}, C., {Bailey}, S., {Barger},
  % K.~A., {Barrera-Ballesteros}, J., {Bartosz}, C., {Bates}, D., {Baumgarten},
  % F., {Bautista}, J., {Beaton}, R., {Beers}, T.~C., {Belfiore}, F., {Bender},
  % C.~F., {Berlind}, A.~A., {Bernardi}, M., {Beutler}, F., {Bird}, J.~C.,
  % {Bizyaev}, D., {Blanc}, G.~A., {Blomqvist}, M., {Bolton}, A.~S., {Boquien},
  % M., {Borissova}, J., {van den Bosch}, R., {Bovy}, J., {Brandt}, W.~N.,
  % {Brinkmann}, J., {Brownstein}, J.~R., {Bundy}, K., {Burgasser}, A.~J.,
  % {Burtin}, E., {Busca}, N.~G., {Cappellari}, M., {Delgado Carigi}, M.~L.,
  % {Carlberg}, J.~K., {Carnero Rosell}, A., {Carrera}, R., {Chanover}, N.~J.,
  % {Cherinka}, B., {Cheung}, E., {G{\'o}mez Maqueo Chew}, Y., {Chiappini}, C.,
  % {Doohyun Choi}, P., {Chojnowski}, D., {Chuang}, C.-H., {Chung}, H.,
  % {Cirolini}, R.~F., {Clerc}, N., {Cohen}, R.~E., {Comparat}, J., {da Costa},
  % L., {Cousinou}, M.-C., {Covey}, K., {Crane}, J.~D., {Croft}, R.~A.~C.,
  % {Cruz-Gonzalez}, I., {Garrido Cuadra}, D., {Cunha}, K., {Damke}, G.~J.,
  % {Darling}, J., {Davies}, R., {Dawson}, K., {de la Macorra}, A., {Dell'Agli},
  % F., {De Lee}, N., {Delubac}, T., {Di Mille}, F., {Diamond-Stanic}, A.,
  % {Cano-D{\'{\i}}az}, M., {Donor}, J., {Jos{\'e} Downes}, J., {Drory}, N., {du
  % Mas des Bourboux}, H., {Duckworth}, C.~J., {Dwelly}, T., {Dyer}, J.,
  % {Ebelke}, G., {Eigenbrot}, A.~D., {Eisenstein}, D.~J., {Emsellem}, E.,
  % {Eracleous}, M., {Escoffier}, S., {Evans}, M.~L., {Fan}, X.,
  % {Fern{\'a}ndez-Alvar}, E., {Fernandez-Trincado}, J.~G., {Feuillet}, D.~K.,
  % {Finoguenov}, A., {Fleming}, S.~W., {Font-Ribera}, A., {Fredrickson}, A.,
  % {Freischlad}, G., {Frinchaboy}, P.~M., {Fuentes}, C.~E., {Galbany}, L.,
  % {Garcia-Dias}, R., {Garc{\'{\i}}a-Hern{\'a}ndez}, D.~A., {Gaulme}, P.,
  % {Geisler}, D., {Gelfand}, J.~D., {Gil-Mar{\'{\i}}n}, H., {Gillespie}, B.~A.,
  % {Goddard}, D., {Gonzalez-Perez}, V., {Grabowski}, K., {Green}, P.~J.,
  % {Grier}, C.~J., {Gunn}, J.~E., {Guo}, H., {Guy}, J., {Hagen}, A., {Hahn}, C.,
  % {Hall}, M., {Harding}, P., {Hasselquist}, S., {Hawley}, S.~L., {Hearty}, F.,
  % {Gonzalez Hern{\'a}ndez}, J.~I., {Ho}, S., {Hogg}, D.~W.,
  % {Holley-Bockelmann}, K., {Holtzman}, J.~A., {Holzer}, P.~H., {Huehnerhoff},
  % J., {Hutchinson}, T.~A., {Hwang}, H.~S., {Ibarra-Medel}, H.~J., {da Silva
  % Ilha}, G., {Ivans}, I.~I., {Ivory}, K., {Jackson}, K., {Jensen}, T.~W.,
  % {Johnson}, J.~A., {Jones}, A., {J{\"o}nsson}, H., {Jullo}, E., {Kamble}, V.,
  % {Kinemuchi}, K., {Kirkby}, D., {Kitaura}, F.-S., {Klaene}, M., {Knapp},
  % G.~R., {Kneib}, J.-P., {Kollmeier}, J.~A., {Lacerna}, I., {Lane}, R.~R.,
  % {Lang}, D., {Law}, D.~R., {Lazarz}, D., {Lee}, Y., {Le Goff}, J.-M., {Liang},
  % F.-H., {Li}, C., {Li}, H., {Lian}, J., {Lima}, M., {Lin}, L., {Lin}, Y.-T.,
  % {Bertran de Lis}, S., {Liu}, C., {de Icaza Lizaola}, M.~A.~C., {Long}, D.,
  % {Lucatello}, S., {Lundgren}, B., {MacDonald}, N.~K., {Deconto Machado}, A.,
  % {MacLeod}, C.~L., {Mahadevan}, S., {Geimba Maia}, M.~A., {Maiolino}, R.,
  % {Majewski}, S.~R., {Malanushenko}, E., {Malanushenko}, V., {Manchado}, A.,
  % {Mao}, S., {Maraston}, C., {Marques-Chaves}, R., {Masseron}, T., {Masters},
  % K.~L., {McBride}, C.~K., {McDermid}, R.~M., {McGrath}, B., {McGreer}, I.~D.,
  % {Medina Pe{\~n}a}, N., {Melendez}, M., {Merloni}, A., {Merrifield}, M.~R.,
  % {Meszaros}, S., {Meza}, A., {Minchev}, I., {Minniti}, D., {Miyaji}, T.,
  % {More}, S., {Mulchaey}, J., {M{\"u}ller-S{\'a}nchez}, F., {Muna}, D.,
  % {Munoz}, R.~R., {Myers}, A.~D., {Nair}, P., {Nandra}, K., {Correa do
  % Nascimento}, J., {Negrete}, A., {Ness}, M., {Newman}, J.~A., {Nichol}, R.~C.,
  % {Nidever}, D.~L., {Nitschelm}, C., {Ntelis}, P., {O'Connell}, J.~E.,
  % {Oelkers}, R.~J., {Oravetz}, A., {Oravetz}, D., {Pace}, Z., {Padilla}, N.,
  % {Palanque-Delabrouille}, N., {Alonso Palicio}, P., {Pan}, K., {Parejko},
  % J.~K., {Parikh}, T., {P{\^a}ris}, I., {Park}, C., {Patten}, A.~Y., {Peirani},
  % S., {Pellejero-Ibanez}, M., {Penny}, S., {Percival}, W.~J., {Perez-Fournon},
  % I., {Petitjean}, P., {Pieri}, M.~M., {Pinsonneault}, M., {Pisani}, A.,
  % {Poleski}, R., {Prada}, F., {Prakash}, A., {Queiroz}, A.~B.~d.~A., {Raddick},
  % M.~J., {Raichoor}, A., {Barboza Rembold}, S., {Richstein}, H., {Riffel},
  % R.~A., {Riffel}, R., {Rix}, H.-W., {Robin}, A.~C., {Rockosi}, C.~M.,
  % {Rodr{\'{\i}}guez-Torres}, S., {Roman-Lopes}, A., {Rom{\'a}n-Z{\'u}{\~n}iga},
  % C., {Rosado}, M., {Ross}, A.~J., {Rossi}, G., {Ruan}, J., {Ruggeri}, R.,
  % {Rykoff}, E.~S., {Salazar-Albornoz}, S., {Salvato}, M., {S{\'a}nchez}, A.~G.,
  % {Aguado}, D.~S., {S{\'a}nchez-Gallego}, J.~R., {Santana}, F.~A., {Santiago},
  % B.~X., {Sayres}, C., {Schiavon}, R.~P., {da Silva Schimoia}, J., {Schlafly},
  % E.~F., {Schlegel}, D.~J., {Schneider}, D.~P., {Schultheis}, M., {Schuster},
  % W.~J., {Schwope}, A., {Seo}, H.-J., {Shao}, Z., {Shen}, S., {Shetrone}, M.,
  % {Shull}, M., {Simon}, J.~D., {Skinner}, D., {Skrutskie}, M.~F., {Slosar}, A.,
  % {Smith}, V.~V., {Sobeck}, J.~S., {Sobreira}, F., {Somers}, G., {Souto}, D.,
  % {Stark}, D.~V., {Stassun}, K., {Stauffer}, F., {Steinmetz}, M.,
  % {Storchi-Bergmann}, T., {Streblyanska}, A., {Stringfellow}, G.~S.,
  % {Su{\'a}rez}, G., {Sun}, J., {Suzuki}, N., {Szigeti}, L., {Taghizadeh-Popp},
  % M., {Tang}, B., {Tao}, C., {Tayar}, J., {Tembe}, M., {Teske}, J., {Thakar},
  % A.~R., {Thomas}, D., {Thompson}, B.~A., {Tinker}, J.~L., {Tissera}, P.,
  % {Tojeiro}, R., {Hernandez Toledo}, H., {de la Torre}, S., {Tremonti}, C.,
  % {Troup}, N.~W., {Valenzuela}, O., {Martinez Valpuesta}, I.,
  % {Vargas-Gonz{\'a}lez}, J., {Vargas-Maga{\~n}a}, M., {Vazquez}, J.~A.,
  % {Villanova}, S., {Vivek}, M., {Vogt}, N., {Wake}, D., {Walterbos}, R.,
  % {Wang}, Y., {Weaver}, B.~A., {Weijmans}, A.-M., {Weinberg}, D.~H.,
  % {Westfall}, K.~B., {Whelan}, D.~G., {Wild}, V., {Wilson}, J., {Wood-Vasey},
  % W.~M., {Wylezalek}, D., {Xiao}, T., {Yan}, R., {Yang}, M., {Ybarra}, J.~E.,
  % {Y{\`e}che}, C., {Zakamska}, N., {Zamora}, O., {Zarrouk}, P., {Zasowski}, G.,
  % {Zhang}, K., {Zhao}, G.-B., {Zheng}, Z., {Zheng}, Z., {Zhou}, X., {Zhou},
  % Z.-M., {Zhu}, G.~B., {Zoccali}, M., and {Zou}, H. 
  2017, 
  \textit{{Sloan
   Digital Sky Survey IV: Mapping the Milky Way, Nearby Galaxies, and the
  Distant Universe}}, \aj, 154, 28.
\item  {Roig}, B., {Blanton}, M.~R., and {Ross}, N.~P. 2014,
  \textit{{Unusual Broad-line Mg II Emitters among Luminous Galaxies in the
  Baryon Oscillation Spectroscopic Survey}}, \apj, 781, 72.
\item 
 {Zhu}, G., {Blanton}, M.~R., {Burles}, S.~M., {Coil}, A.~L.,
  {Cool}, R.~J., {Eisenstein}, D.~J., {Moustakas}, J., {Wong}, K.~C., and
  {Aird}, J. 2011, \textit{{PRIMUS: Obscured Star Formation on the Red
  Sequence}}, \apj, 726, 110
\item {Blanton}, M.~R., {Kazin}, E., {Muna}, D., {Weaver}, B.~A., and
  {Price-Whelan}, A. 2011, \textit{{Improved Background Subtraction for the
  Sloan Digital Sky Survey Images}}, \aj, 142, 31.
\item 
Blanton, M.~R. and Roweis, S. (2007), {\it $K$-corrections and filter
transformations in the ultraviolet, optical, and near-infrared}, \aj,
133, 734
\end{ditemize}

\vspace{-8pt}
\subsection*{\normalsize Performance in
  Prior Research Efforts:}
\begin{ditemize}\setlength{\itemsep}{0pt}
\item SDSS-IV Director (2012--2022): successful in leading project
  through fund-raising, development, and 6.5 years of operations. 
\item SDSS-III Data Coordinator (2007--2013): successfully led
  development of data management systems and data releases for
  SDSS-III.
\item Freely distributed New York University Value-Added Galaxy
  Catalog, used in over 1,000 refereed publications (2005--present), and
  the NASA-Sloan Atlas, used in over 300 refereed publications
  (2012--present).
\item Wrote and distributed freely a widely used code to fit stellar
  population models to galaxy flux observations, known as
  \texttt{kcorrect}, used in over 1,000 refereed publications
  (2002--present).
\end{ditemize}


\clearpage
\section{Current \& Pending Support}\label{sec:support}

\noindent \underline{PI Blanton: Current Support}

\begin{itemize*}
\item[]{Title: {\em Meta-study of UV-through-NIR Explosive Transients for the Roman Space
Telescope and Beyond}}
\item[]{Source: NASA}
\item[]{Location: New York University}
%\item[]{Program officer: Dr. Peter Kurczynski, pkurczyn@nsf.gov, (703) 292-7248}
\item[]{Amount: \$547,513}
\item[]{Period: 01/21/2022 through 01/20/2025}
\item[]{Commitment: 0.0 months FTE per year (0.0 person-years)}
\item[]{Statement: Not related to the proposed project. PI of record while
grant is transferred to original PI at University of Virginia.}
\end{itemize*}

\begin{itemize*}
\item[]{Title: {\em Probing external accretion  through the stellar
    counter-rotation phenomena.}}
\item[]{Source: NASA JPL}
\item[]{Location: New York University}
%\item[]{Program officer: Dr. Peter Kurczynski, pkurczyn@nsf.gov, (703) 292-7248}
\item[]{Amount: \$14,850}
\item[]{Period: 03/09/2023 through 03/08/2025}
\item[]{Commitment: 0.0 months FTE per year (0.0 person-years)}
\item[]{Statement: Not related to the proposed project}
\end{itemize*}

\begin{itemize*}
\item[]{Title: {\em Expanding the Impact of the Center for Cosmology
    and Particle Physics Visitor Program}}
\item[]{Source: Alfred P. Sloan Foundation}
\item[]{Location: New York University}
%\item[]{Program officer: Dr. Peter Kurczynski, pkurczyn@nsf.gov, (703) 292-7248}
\item[]{Amount: \$50,000}
\item[]{Period: 07/01/2022 through 06/30/2024}
\item[]{Commitment: 0.0 months FTE}
\item[]{Statement: Not related to the proposed project}
\end{itemize*}

\begin{itemize*}
\item[]{Title: {\em MOS Observation Support for SDSS-V}}
\item[]{Source: Astrophysical Research Consortium}
\item[]{Location: New York University}
%\item[]{Program officer: Dr. Peter Kurczynski, pkurczyn@nsf.gov, (703) 292-7248}
\item[]{Amount: \$45,580}
\item[]{Period: 05/15/2022 through 07/01/2023}
\item[]{Commitment: 2.0 months FTE}
\item[]{Statement: Not related to the proposed project}
\end{itemize*}

\noindent \underline{PI Blanton: Pending Support}

\begin{itemize*}
\item[]{Title: {\em MOS Observation Support for SDSS-V}}
\item[]{Source: Astrophysical Research Consortium}
\item[]{Location: New York University}
%\item[]{Program officer: Dr. Peter Kurczynski, pkurczyn@nsf.gov, (703) 292-7248}
\item[]{Amount: \$47,799.38}
\item[]{Period: 07/01/2023 through 12/31/2023}
\item[]{Commitment: 2.0 months FTE}
\item[]{Statement: Not related to the proposed project}
\end{itemize*}

%\begin{itemize*}
%\item[]{Title: {\em A comprehensive multiwavelength census of low
    %redshift active galactic nuclei}}
%\item[]{Source: National Science Foundation}
%\item[]{Location: New York University}
%%\item[]{Program officer: Dr. Peter Kurczynski, pkurczyn@nsf.gov, (703) 292-7248}
%\item[]{Amount: \$470,552}
%\item[]{Period: 07/01/2023 through 06/30/2026}
%\item[]{Commitment: 1.0 months FTE}
%\item[]{Statement: Related but distinct work on active galactic
  %nuclei}
%\end{itemize*}

%\begin{itemize*}
%\item[]{Title: {\em Archaeology of galaxies: understanding dust
    %attenuation from radiative transfer in simulated galaxies}}
%\item[]{Source: National Science Foundation}
%\item[]{Location: New York University}
%%\item[]{Program officer: Dr. Peter Kurczynski, pkurczyn@nsf.gov, (703) 292-7248}
%\item[]{Amount: \$282,571}
%\item[]{Period: 07/01/2023 through 06/30/2025}
%\item[]{Commitment: 1.0 months FTE}
%\item[]{Statement: Not related to the proposed project}
%\end{itemize*}

\clearpage
\section{Budget Narrative}\label{sec:budget}

\noindent {\bf Senior Personnel:} The PI is requesting 1.0 month of
summer salary for each of the 2 years of the project.  The PI is
responsible for the overall management of the project. The PI will
supervise the GRA and undergraduate and will assist in the writing,
data analysis, and interpretation.

\noindent {\bf Other Personnel:} Graduate Research Assistant (GRA):
Funds are requested for 2 academic years (AY) plus 2 summers. The GRA
will develop the software and perform the analysis described in the
proposal. Undergraduate Research Assistant (UGRA): Funds are requested
for an hourly research position. The UGRA will work with the GRA and
assist in the data analysis and data vetting.

\noindent {\bf Fringe Benefits Rate:} A fringe benefits rate 
of 31\% applies to the PI salary and the undergraduate student salary.

\noindent {\bf Capital Equipment:} Funds are requested in Year 1 for 
dedicated computer  servers with which to perform the analysis (\$5,000 each
for two Dell PowerEdge R7525 Servers, with 2 16-core processers with 128M 
of cache, 4 Tb of local disk,  and 64 Gb of memory).

\noindent {\bf Domestic Travel:} Funds are requested for attendance at
one domestic conference for the GRA in each year. We assume \$1500 for
a 4-day conference (\$200 for registration fee, \$500 for airfare,
\$150/night for lodging, and \$50/night per diem).

\noindent {\bf Foreign Travel:} Funds are requested for attendance at
one foreign conference for the GRA in each year. For each conference
we assume \$1500 for a 4-day conference (\$200 for registration fee,
\$500 for airfare, \$150/night for lodging, and \$50/night per diem).

\noindent {\bf Publications:} We anticipate two 10-page journal
articles each year. Based on prior experience with the AAS Journals,
the typical publication cost will be \$1500 per paper in 2023 dollars.

\noindent {\bf Other Direct Costs:} Graduate students receive tuition
remission charged at 37\% of graduate student salary in lieu of fringe
benefits.

\noindent {\bf Rates:} Senior personnel salaries increase 4\%
annually, while OTPS costs increase 2.5\% per year.

\noindent {\bf Indirect Costs:} An indirect cost rate has been
negotiated with DHHS, agreement dated October 6, 2021.  The agreed
upon rate for Facilities and Administration costs (F\&A) is 61\% as of
FY 2024 and thereafter.  The MTDC base excludes capital equipment,
tuition remission, participant support costs, and subcontracts beyond
the first \$25,000.

\end{document}


